---
title: "Learn Basics of Data Analysis using R "
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
date: "`r format(Sys.time(), '%d %B %Y')`"
subtitle: School of Economics, Quaid-i-Azam University
header-includes:
  - \usepackage{titling}
  - \pretitle{
       \begin{center}
        \hspace*{-16cm}
        \includegraphics[width=1.5in,height=1.5in]{logo.jpg}\LARGE\\
        \vspace*{-3cm}
         }
---

## [Look at all the data points](https://www.rstudio.com/blog/how-i-use-stories-to-share-data-at-meetings/#.Ysv3S4zF4fE.twitter)

In Penguin data, there are variables that specify measurements

```{r}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```

I’m curious about differences in measurements, so I plot the bill length, bill depth, and flipper length. I use a scatter plot because I want to see each data point. I also color the points by species, based on the hunch that different species have different measurements:

```{r}
ggplot(penguins)+aes(x=body_mass_g,y=bill_length_mm, color=species)+
  geom_point()+labs(title = "Bill Length by Species")

```

```{r}
ggplot(penguins, 
       aes(x = body_mass_g, 
           y = bill_depth_mm, 
           color = species)) + 
  geom_point() + 
  labs(title = "Bill Depth By Species")

```

```{r}
ggplot(penguins, 
       aes(x = body_mass_g, 
           y = flipper_length_mm, 
           color = species)) + 
  geom_point() + 
  labs(title = "Flipper Length By Species")

```

**Average length of these measurements by penguin species:**

```{r}
penguins |> 
  group_by(species) |> 
  summarize(mean_bill_length = 
              mean(bill_length_mm, na.rm = TRUE), 
            mean_bill_depth = 
              mean(bill_depth_mm, na.rm = TRUE), 
            mean_flipper_length = 
              mean(flipper_length_mm, na.rm = TRUE), 
            mean_body_mass = 
              mean(body_mass_g, na.rm = TRUE))
```


## Categorize Details into Interesting Themes

Patterns in species measurements
Differences, but also similarities
The Chinstrap penguins trade bill size for flipper size

## The Presentation: Start with the Story
Here’s how I would present the information:

Point out interesting themes
Describe selected details
Show selected data points

## Point out interesting Themes
 
## Describe Selected Details

## Show Selected Data Points